---
title: "Hypothesis Testing"
author: "Enqun Wang (EW), Yiyan Zhou (YZ)"
date: "April 26, 2016"
output: html_document
---

#### Exploratory Data Analysis

According to the exploratory data analysis, we decide to first elect variables as follows,

|Product Factor |Promotion Factor |Platform Factor |Market Factor|
|--------|--------|--------|--------|
|1. Rate of Return |1. LB Received |1. Balance |1. R.007 |
|2. Term |2. LB Used |2. Capital Inflow | |
|3. TZD Account| | | |



```{r message=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
setwd("/Users/zhouyiyan/Documents/STAA568 Topics in Industrial Organizational Statistics/DMAIC/Case Study/3-Analyze")

require(dplyr)

data = data.frame(read.csv("data.csv", header = T)[-c(1:6),-c(1:3)])
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
# center data
require(caret)
 
trans = preProcess(data, c("center", "scale"))
df = data.frame(trans = predict(trans, data))
```


We use the centered data to test the significance of the variables, and find the significant ones.


1. Increase.Rate.5Day ~ Rate.of.Return

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.1 = lm(df$trans.Increase.Rate.5Day ~ df$trans.Rate.of.Return)
summary(model.1)
```

The p value of the test is 0.9635, which is greater than 0.05. We should not reject the null hypothesis and conclude that the coefficient of Rate.of.Return is not significant.



2. Increase.Rate.5Day ~ Term

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.2 = lm(df$trans.Increase.Rate.5Day ~ df$trans.Term)
summary(model.2)
```


The p value of the test is 0.1773, which is greater than 0.05. We should not reject the null hypothesis and conclude that the coefficient of Term is not significant.


3. Increase.Rate.5Day ~ TZD.Account

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.3 = lm(df$trans.Increase.Rate.5Day ~ df$trans.TZD.Account)
summary(model.3)
```

The p value of the test is 0.009031, which is less than 0.05. We should reject the null hypothesis and conclude that the coefficient of TZD.Account is significant.




4. Increase.Rate.5Day ~ LB.Received

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.4 = lm(df$trans.Increase.Rate.5Day ~ df$trans.LB.Received)
summary(model.4)
```


The p value of the test is 0.04645, which is less than 0.05. We should reject the null hypothesis and conclude that the coefficient of LB.Received is significant.


5. Increase.Rate.5Day ~ LB.Used

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.5 = lm(df$trans.Increase.Rate.5Day~df$trans.LB.Used)
summary(model.5)
```


The p value of the test is 0.1695, which is greater than 0.05. We should not reject the null hypothesis and conclude that the coefficient of LB.Used is not significant.



6. Increase.Rate.5Day ~ Balance

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.6 = lm(df$trans.Increase.Rate.5Day~df$trans.Balance)
summary(model.6)
```

The p value of the test is 0.8785, which is greater than 0.05. We should not reject the null hypothesis and conclude that the coefficient of Balanec is not significant.



7. Increase.Rate.5Day ~ Capital.Inflow

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.7 = lm(df$trans.Increase.Rate.5Day~df$trans.Capital.Inflow)
summary(model.7)
```

The p value of the test is 5.467e-05, which is less than 0.05. We should reject the null hypothesis and conclude that the coefficient of Capital.Inflow is significant.


8. Increase.Rate.5Day ~ R.007

```{r, echo=FALSE, message=FALSE, warning=FALSE}
model.8 = lm(df$trans.Increase.Rate.5Day~df$trans.R.007)
summary(model.8)
```

The p value of the test is 0.03061, which is less than 0.05. We should reject the null hypothesis and conclude that the coefficient of R.007 is significant.


To sum up, LB.Received, Capital.Inflow, TZD.Account and R.007 are four significant variables.

Considering the above four significant the variables, we do model selection by forward stepwise.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(leaps)

model = regsubsets(df$trans.Increase.Rate.5Day ~ df$trans.LB.Received + df$trans.Capital.Inflow + df$trans.TZD.Account + df$trans.R.007, data=df, method = "forward")
summary(model)
```


It seems that the capital inflow is the most significent. We can now select the best model based on the voice of customer. 

The importance of the four variables are as followed:

|Importance|Variable|
|---|---|
|1|Capital Inflow|
|2|Lucky Bag Received|
|3|R 007|
|4|The Financial Product TZD Account|